Long-term cloud enhancement events of global solar irradiance over Thessaloniki, Greece

### 2024-07-10 article/article.Rmd
Commit 2024-07-10 10:14

The distribution of the number of CE events as a function of OIR is shown in
Figure\nobreakspace{}\ref{fig:ovir-distribution}. Apparently, there is an inverse
relationship between the frequency of CE events and OIR with an exponential-like
decline. This is expected, as the stronger the CE events are, the rarer the
conditions favoring the occurrence of CE events. For the majority (over $62\,\%$) of
the CE events the OIR is below the long-term average of
$`r round(mean(ST_E_yearly$GLB_diff.mean), 1)` \, \text{W} / \text{m}^2$,
while about $8.1\,\%$ of the events correspond to OIR larger than
$100\,\text{W}/\text{m}^2$ and up to the highest value of $412.4\,\text{W}/\text{m}^2$.
This distribution is indicative of the magnitude and the probability of the expected
CE events over Thessaloniki.  Similar distribution of CE events, albeit with larger
OIR values, has been reported by @Vamvakas2020, for the city of Patras. This site is
located $2.5^\circ$ south of Thessaloniki and is exposed to air masses coming mainly
from the eastern Mediterranean resulting in different cloud patterns, that may affect
the characteristics and magnitude of the CE events.

@@

```{r ceg-duration-distribution, echo=FALSE, fig.cap="Relative frequency distribution of CE groups of consequent CE events according to their duration for Thessaloniki in the period 1993 -- 2023."}
knitr::include_graphics("../images/groups-1.png")
```

>>>>

The distribution of the number of CE events as a function of OIR is shown in
Figure\nobreakspace{}\ref{fig:ovir-distribution}.  Apparently, there is an inverse
relationship between the frequency of CE events and OIR with an exponential-like
decline. This is expected, as the stronger the CE events are, the rarer the
conditions favoring the occurrence of CE events.  For the majority (over $62\,\%$) of
the CE events the OIR is below the long-term average of
$`r round(mean(ST_E_yearly$GLB_diff.mean),1)`\,\text{W}/\text{m}^2$, while about
$8.1\,\%$ of the events correspond to OIR larger than $100\,\text{W}/\text{m}^2$ and
up to the highest value of $412.4\,\text{W}/\text{m}^2$.  This distribution is
indicative of the magnitude and the probability of the expected CE events over
Thessaloniki.  Similar distribution of CE events, albeit with larger OIR values, has
been reported by @Vamvakas2020, for the city of Patras. This site is located
$2.5^\circ$ south of Thessaloniki and is exposed to air masses coming mainly from the
eastern Mediterranean resulting in different cloud patterns, that may affect the
characteristics and magnitude of the CE events.

@@

```{r ceg-duration-distribution, echo=FALSE, fig.cap="Relative frequency distribution of CE groups of consequent CE events according to their duration for Thessaloniki in the period 1993 -- 2023. The histogram was split in two plots with different y-axis scales for better readability."}
# knitr::include_graphics("../images/groups-1.png")
knitr::include_graphics("../images/groups-7.png")
```
